Deep Probabilistic Models for Camera Geo-Calibration

### 2018-12-06 dissertation.tex
add discussion section
disscussion
add vita to dissertation
put orcid in the front page
include acknowledgment

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{xspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{memhfixc}
\usepackage{algorithm2e, algorithmic}
\usepackage{soul}
\usepackage{multirow}
\usepackage{miscstyle}

@@

\author{Menghua Zhai}
%\title{Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration}
%\title{Statistical Models for Camera Geo-Calibration}
\title{Deep Probabilistic Models for Camera Geo-Calibration}

@@

%\begin{acknowledgments}
	%Acknowledge people/things here
%\end{acknowledgments}

@@

\tableofcontents\clearpage
%\listoffigures\clearpage
%\listoftables\clearpage

@@

%\inject{mcmc}
%\inject{fasthorizon}
%\inject{crosstransf}
%\inject{whenwhere}

%\inject{discussion}

@@

%\inject{vita}

>>>>

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{xspace}
%\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{memhfixc}
\usepackage{algorithm2e, algorithmic}
\usepackage{soul}
\usepackage{multirow}
\usepackage{miscstyle}

@@

\author{Menghua Zhai}
\orcid{0000-0001-5874-238X}
\title{Deep Probabilistic Models for Camera Geo-Calibration}

@@

\begin{acknowledgments}
  I would like to express the deepest appreciation to my advisor,
Professor Nathan Jacobs, who not only financed my Ph.D. career, but
also supported my research with his profound insight
and knowledge. Over the years I have benefited from guidance,
expertise, and patience. I have also learned a lot from his efficient
work style and the way he attacks problems. I honestly fell lucky to
have had the opportunity to work alongside him and I am proud of what
we have accomplished together.

I would like to take this opportunity to give my thanks to several
individuals who helped me through the path:  Jinze Liu, who
first got me enrolled to the graduate school; 
Qiang Ye, Judy Goldsmith, and Andrew Klapper, for intriguing
my desires for pursuing advanced knowledge. A huge appreciation to the
other members of my advisory committee, Ruigang Yang and Ramakanth
Kavuluru, for their invaluable feedback through my defense.

I have had the privilege of working and collaborating with many
individuals, including: Zachary Bessinger, Tawfiq Salem, Connor
Greenwell, Ryan Baltenberger, Neil Moore, Samuel Schulter, and others.
In the end, I would like to thank my friend and colleague, Scott
Workman, with whom I worked closest and accomplished a great deal of
research projects.
\end{acknowledgments}

@@

\tableofcontents\clearpage
\listoffigures\clearpage
\listoftables\clearpage

@@

\inject{mcmc}
\inject{fasthorizon}
\inject{whenwhere}
\inject{crosstransf}

\inject{discussion}

@@

\inject{vita}
